---
output: github_document
always_allow_html: yes
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
knitr::opts_chunk$set(echo = TRUE)
k_path_project <<- tryCatch(rprojroot::find_rstudio_root_file(), error = function(e) getwd())
library(kableExtra)
library(magrittr)
library(readr)

badge_custom <- function(key, value, color, url = NULL){
    alt <- paste(key)
    key <- gsub(" ", "%20", key)
    value <- gsub(" ", "%20", value)
    key <- gsub("-", "--", key)
    value <- gsub("-", "--", value)
    badge <- paste0("![", alt, "](https://img.shields.io/badge/", key, "-", 
        value, "-", color, ".svg)")
    if (is.null(url)) 
        return(badge)
    paste0("[", badge, "](", url, ")")
}
```

# More for Less: Adaptive Labeling Payments in Online Labor Markets

<!-- badges: start -->
`r badge_custom("Language", "R (3.4.3)", "green")`
<!-- badges: end -->

## Synopsis

In many predictive tasks where human intelligence is needed to label training
instances, online crowdsourcing markets have emerged as promising platforms for
large-scale, cost-effective labeling.

However, these platforms also introduce significant challenges that must be
addressed for these opportunities to materialize.

In particular, it has been shown that different tradeoffs between payment
offered to labelers and the quality of labeling arise at different times,
possibly as a result of different market conditions and even the nature of the
tasks themselves.

Because the underlying mechanism giving rise to different tradeoffs is not well
understood, for any given labeling task and at any given time, it is not known
what labeling payments to offer in the market so as to cost-effectively produce
accurate models.

Importantly, because in these markets the acquired labels are not always
correct, determining the expected effect of labels acquired at any given payment
on the improvement in model performance is particularly challenging.

Effective and robust methods for dealing with these challenges are essential to
enable a growing reliance on these promising and increasingly popular labor
markets for large-scale labeling.

In this paper, we first present this new problem of Adaptive Labeling Payment
(ALP): how to learn and sequentially adapt the payment offered to crowd labelers
before they undertake a labeling task, so as to produce a given predictive
performance cost-effectively. 

We then develop an ALP approach and discuss the key challenges it aims to
address to yield consistently good performance.

We extensively evaluate our approach over a wide variety of market conditions.

Our results demonstrate that the ALP method we propose yields significant cost
savings and robust performance across different settings.

As such, our ALP approach can be used as a benchmark for future mechanisms to
determine cost-effective selection of labeling payments.


## Reproducing the Paper Results

This project was developed and tested under R 3.4.3 for Windows which you can
get [here](https://cran.r-project.org/bin/windows/base/old/3.4.3/). 

All the project essential R packages will be installed automatically when you
first launch the code.

The installed packages versions are exactly as they existed when the code was
developed and tested.

While the project may work on newer versions of R and its packages, we can only
guarantee the reproducibility of the results when the conditions above are met.

## How to Run

1. Download the project from GitHub and unpack it into a local directory.
2. Open R or RStudio and set the working directory to the project root folder.
3. Run **main.R** under the *~/code* folder.

## How it Works

### Inputs

Configuration and execution of the simulations are coded in two separate files:
*config.yml* and *main.R*. Both files are under the *~/code* folder.

The configuration file defines the dataset, scenario and simulation nuances via
[yaml tags](https://yaml.org/spec/1.2/spec.html#id2761292). The tags are
accompanied by explanations about what they define.

The script file named *main.R*, initializes and runs the simulation without
further modification needed.

### Algorithm

See the paper for details about the different algorithms.

## Output

Upon successful completion, each simulation outputs three files (see
[Appendix](#appendix)):

1. [A report table](#report-table) under *~/results/reports*
2. [A metadata table](#metadata-table) under *~/results/metadata*
3. [A ledger table](#ledger-table) under *~/results/ledgers*

While there is some overlap between the tables, the *report* table serves as the
most succinct debrief. The other two tables are exposed the observer to the
decision making process of the algorithm. *metadata* and *ledger* provide
details on what happened on an instance-level and batch-level, respectively.

## Appendix

### Report table
  
```{r, echo=FALSE, out.width = "100%"}
suppressMessages(
    table <- read_csv(file.path(k_path_project, "README_files", "report.csv"))
)
table %>% 
    tail() %>% 
    kable(digits = 2) %>% 
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                              full_width = TRUE,
                              position = "left",
                              font_size = 10)
```

<br>

### Metadata table
   
```{r, echo=FALSE, out.width = "100%"}
suppressMessages(
    table <- read_csv(file.path(k_path_project, "README_files", "metadata.csv"))
)
table %>% 
    tail() %>% 
    kable(digits = 2) %>% 
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                              full_width = TRUE,
                              position = "left",
                              font_size = 10)
```

<br> 

### Ledger table
   
```{r, echo=FALSE, out.width = "100%"}
suppressMessages(
    table <- read_csv(file.path(k_path_project, "README_files", "ledger.csv"))
)
table %>% 
    tail() %>% 
    kable(digits = 2) %>% 
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                              full_width = TRUE,
                              position = "left",
                              font_size = 10)
```


